---
title: "又是元气满满的一天呢"
author: "[闫求识](https://qiushi.rbind.io/)"
date: "`r format(Sys.time(), '%d %B %Y')`"
mail: "565702994@qq.com"
linkedin: "求识-闫-893a48194"
twitter: "Qiushi14252698"
github: "enixam"
logo: "logo.jpg"
bibliography: bib.bib
link-citations: true
biblio-style: "apalike"
#nocite: '@*'
output:
  epuRate::epurate:
    toc: TRUE
    number_sections: FALSE
    code_folding: "show"
---

<br><br>

> Let's start with a short introduction. Explain briefly what this document is going to talk about. May be add a [useful link](https://github.com/holtzy/epuRate) relative to this project.


# Get the data
***
Always start by loading *libraries*. The [tidyverse](https://www.tidyverse.org) is probably the package I use the most. Quite difficult to imagine analysing data without it. It is a good practice to load all the packages in the same time. It allows to know exactly what is needed to reproduce your analysis.
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(rmarkdown)    # You need this library to run this template.
library(epuRate)      # Install with devtools: install_github("holtzy/epuRate", force=TRUE)
```

Then I explain what is my input data and I load it. Here is how it looks like:
```{r}
# Show it:
mtcars %>% head(5)
```

This file has `r nrow(mtcars)` lines and `r ncol(mtcars)` columns. It is ready to be analysed.

<div class = "row">
  
<div class = "col-md-4">
<br><br>Since R Markdown use the [bootstrap framework](https://getbootstrap.com/docs/4.0/layout/grid/) under the hood. It is possible to benefit its powerful grid system. Basically, you can consider that your row is divided in 12 subunits of same width. You can then choose to use only a few of this subunits.
</div>
  
<div class = "col-md-4">
<br><br>Here, I use 3 subunits of size 4 (4x3=12). The last column is used for a plot. You can read more about the grid system [here](bootstrap grid system). I got this result showing the following code in my R Markdown document.
</div>
  
<div class = "col-md-4">
```{r, message=FALSE, echo=FALSE}
ggplot( mtcars, aes(x=mpg)) + geom_histogram(fill="skyblue", alpha=0.5) + theme_minimal()
```
</div>
</div>


# A few analysis
***
Here are 3 version of a [circular barplot](https://www.r-graph-gallery.com/circular-barplot/) that you can find in the [R graph gallery](https://www.r-graph-gallery.com/circular-barplot/). Note that the figure is centered. You can change the size of the plot with **fig.width** and **fig.height**  

## basic
Let's start with a basic version of a circular representation of the data
```{r, warning=FALSE, fig.align='center' }
# Create dataset
data=data.frame(
  individual=paste( "Mister ", seq(1,60), sep=""),
  value=sample( seq(10,100), 60, replace=T)
)

# Set a number of 'empty bar'
empty_bar=10

# Add lines to the initial dataset
to_add = matrix(NA, empty_bar, ncol(data))
colnames(to_add) = colnames(data)
data=rbind(data, to_add)
data$id=seq(1, nrow(data))

# Get the name and the y position of each label
label_data=data
number_of_bar=nrow(label_data)
angle= 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust<-ifelse( angle < -90, 1, 0)
label_data$angle<-ifelse(angle < -90, angle+180, angle)

# Make the plot
p = ggplot(data, aes(x=as.factor(id), y=value)) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(stat="identity", fill="#69b3a2") +
  ylim(-100,120) +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm")
  ) +
  coord_polar(start = 0) +
  geom_text(data=label_data, aes(x=id, y=value+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2.5, angle= label_data$angle, inherit.aes = FALSE )

p
```


## grouped
```{r, warning=FALSE, fig.align='center' }
# Create dataset
data=data.frame(
  individual=paste( "Mister ", seq(1,60), sep=""),
  group=c( rep('A', 10), rep('B', 30), rep('C', 14), rep('D', 6)) ,
  value=sample( seq(10,100), 60, replace=T)
)

# Set a number of 'empty bar' to add at the end of each group
empty_bar=4
to_add = data.frame( matrix(NA, empty_bar*nlevels(data$group), ncol(data)) )
colnames(to_add) = colnames(data)
to_add$group=rep(levels(data$group), each=empty_bar)
data=rbind(data, to_add)
data=data %>% arrange(group)
data$id=seq(1, nrow(data))

# Get the name and the y position of each label
label_data=data
number_of_bar=nrow(label_data)
angle= 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust<-ifelse( angle < -90, 1, 0)
label_data$angle<-ifelse(angle < -90, angle+180, angle)

# Make the plot
p = ggplot(data, aes(x=as.factor(id), y=value, fill=group)) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(stat="identity", alpha=0.5) +
  ylim(-100,120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm")
  ) +
  coord_polar() +
  geom_text(data=label_data, aes(x=id, y=value+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2.5, angle= label_data$angle, inherit.aes = FALSE )

p
```

## complex
```{r, warning=FALSE, fig.align='center' }
# Create dataset
data=data.frame(
  individual=paste( "Mister ", seq(1,60), sep=""),
  group=c( rep('A', 10), rep('B', 30), rep('C', 14), rep('D', 6)) ,
  value=sample( seq(10,100), 60, replace=T)
)

# Set a number of 'empty bar' to add at the end of each group
empty_bar=3
to_add = data.frame( matrix(NA, empty_bar*nlevels(data$group), ncol(data)) )
colnames(to_add) = colnames(data)
to_add$group=rep(levels(data$group), each=empty_bar)
data=rbind(data, to_add)
data=data %>% arrange(group)
data$id=seq(1, nrow(data))

# Get the name and the y position of each label
label_data=data
number_of_bar=nrow(label_data)
angle= 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust<-ifelse( angle < -90, 1, 0)
label_data$angle<-ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data=data %>%
  group_by(group) %>%
  summarize(start=min(id), end=max(id) - empty_bar) %>%
  rowwise() %>%
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data = base_data
grid_data$end = grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start = grid_data$start - 1
grid_data=grid_data[-1,]

# Make the plot
p = ggplot(data, aes(x=as.factor(id), y=value, fill=group)) +       # Note that id is a factor. If x is numeric, there is some space between the first bar

  geom_bar(aes(x=as.factor(id), y=value, fill=group), stat="identity", alpha=0.5) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +

  # Add text showing the value of each 100/75/50/25 lines
  annotate("text", x = rep(max(data$id),4), y = c(20, 40, 60, 80), label = c("20", "40", "60", "80") , color="grey", size=3 , angle=0, fontface="bold", hjust=1) +

  geom_bar(aes(x=as.factor(id), y=value, fill=group), stat="identity", alpha=0.5) +
  ylim(-100,120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm")
  ) +
  coord_polar() +
  geom_text(data=label_data, aes(x=id, y=value+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2.5, angle= label_data$angle, inherit.aes = FALSE ) +

  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)

p
```



# Conclusion
***
Read more about this template [here](https://github.com/holtzy/epuRate).

Learn how to custom your R Markdown document [here](https://holtzy.github.io/Pimp-my-rmd/).
